---
title: "Course Project: Exploring Plot Colors"
author: "Zachary Sharrow"
date: "7/18/2019"
output: slidy_presentation
---

```{r, include = F}
library(ggplot2)
```

## Rationale  
  
In Exploratory Data Analysis, we learned about the importance of exploratory
visualizations, and how one useful method is to plot variables of interest, then
add color in order to investigate possible relationships. My app provides an
interactive way to explore some aspects of R's built-in `state` data sets.

## Implementation  
  
The server-side code plots the state data for high school graudation rate (X axis)
against the per capita income (Y axis) for each state, then colors the points
according to which additional variable the user selects from a drop-down menu. 
  
```{r, eval = F}
data(state)
states <- data.frame(state.x77)
states$Region <- state.region
states$Division <- state.division

server <- function(input, output) {
    output$finalPlot <- renderPlot({
        finalPlot <- ggplot(states, aes(HS.Grad, Income, color = states[[input$select]])) +
            xlab("High School Graduation Percentage") + ylab("Per Capita Income") +
            ggtitle("US States, Educational Attainment vs. Income") + 
            geom_point(size = 3) + labs(color = input$select)
        finalPlot
        
    })
}
```
  
Advance to the next slide to see an example of the output, colored by the `Region` variable.  
  
## Example   
  
```{r, echo = F}
data(state)
states <- data.frame(state.x77)
states$Region <- state.region
states$Division <- state.division

finalPlot <- ggplot(states, aes(HS.Grad, Income, color = states[["Region"]])) +
    xlab("High School Graduation Percentage") + ylab("Per Capita Income") +
    ggtitle("US States, Educational Attainment vs. Income") + 
    geom_point(size = 3) + labs(color = "Region")
finalPlot
```
   
## More info  
  
See the project live on [shinyapps.io](https://shackary.shinyapps.io/ddp-week4/)  
  
View source code on [GitHub](https://github.com/shackary/ddp-project)
